Turbulence and Particle Acceleration in Giant Radio Halos: the Origin of Seed Electrons

### 2016-05-01 paper.tex
Added files via upload

Given a seed population of CRs, we adopt essentially the same set of
plasma physics assumptions as the reacceleration model for RHs
\citep{brunetti07,brunetti11}. We solve the isotropic, gyro-phase
averaged Fokker-Planck equation (via a Crank-Nicholson scheme) for the
time evolution of the CRe distribution in the Lagrangian frame
\citep{brunetti07,brunetti11}:
\begin{eqnarray}
{{d f_{\rmn{e}}(p,t)}\over{d t}} &\!=&
\frac{\partial}{\partial p}
\left\{
f_{\rmn{e}}(p,t)\left[
\left|\frac{dp}{dt}\right|_{\rm Coul} 
+ \frac{p}{3}\left(\bnabla\bcdot \bvel\right)
+ \left|\frac{dp}{dt}\right|_{\rm rad}\right.\right.
\nonumber\\
&-& \left.\left.{1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right) 
\right]\right\} - \left(\bnabla\bcdot \bvel\right) f_{\rmn{e}}(p,t)
\nonumber\\
&+& {{\partial^2 }\over{\partial p^2}}
\left[
D_{pp} f_{\rmn{e}}(p,t) \right]+ Q_{\rmn{e}}\left[p,t;f_{\rmn{p}}(p,t)\right]   \, .
\label{elettroni}
\end{eqnarray}
Here $f_{\rmn{e}}$ is the one-dimensional distribution in position $x$
(suppressed for clarity), momentum $p$ and time $t$ (which is
normalized such that the number density is given by
$n_{\rmn{e}}(t)=\int d p f_{\rmn{e}}(p,t)$), $d/dt=\partial/\partial
t+\bvel\bcdot\bnabla$ is the Lagrangian derivative, $\bvel$ is the gas
velocity, $|dp/dt|$ represents radiative (rad) and Coulomb (Coul)
losses, \AP{please insert formulae:}
\begin{eqnarray}
  \left|\frac{dp}{dt}\right|_{\rm Coul}
  &=& \\
  \left|\frac{dp}{dt}\right|_{\rm rad~}
  &=& 
\end{eqnarray}
$D_{pp}$ is the momentum space diffusion coefficient (see
Sect.~\ref{sec:reacc}), and $Q_{\rmn{e}}$ denotes the injection rate
of primary and secondary electrons in the ICM (see
Sect.~\ref{sec:cosmo_sim}). The first term containing the expression
$\bnabla\bcdot \bvel$ represents Fermi-I acceleration and the second
term of this form describes adiabatic gains and losses.

@@

The time evolution of the spectral energy distribution of CRps,
$f_{\rmn{p}}$, is similarly given by:
\begin{eqnarray}
\lefteqn{
  {{d f_{\rmn{p}}(p,t)}\over{d t}} =
  {{\partial }\over{\partial p}}
  \left\{
  f_{\rmn{p}}(p,t)\left[ \left|{{dp}\over{dt}}\right|_{\rm Coul}
    + \frac{p}{3}\bnabla\bcdot \left(\bvel+\bvel_{\rmn{st}}\right)\right.\right.}
\nonumber\\
&&-\left.\left. {1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right)
\right]\right\} - f_{\rmn{p}}(p,t) \bnabla\bcdot \left(\bvel+\bvel_{\rmn{st}}\right) 
- \bvel_{\rmn{st}}\bcdot\bnabla f_{\rmn{p}}(p,t)
\nonumber\\
&&+\,\,\, {{\partial^2 }\over{\partial p^2}}
\left[ D_{pp} f_{\rmn{p}}(p,t) \right] - {{f_{\rmn{p}}(p,t)}\over{\tau_{\rm had}(p)}}
+ Q_{\rmn{p}}(p,t)\, ,
\label{eq:FP_p}
\end{eqnarray}
where $\bvel_{\rmn{st}}=-\varv_{\rmn{A}}\bnabla f_{\rmn{p}}/|\bnabla
f_{\rmn{p}}|$ is the streaming velocity in the isotropic transport
approximation, $\varv_{\rmn{A}}$ is the Alfv\'en speed,
$Q_{\rmn{p}}(p,t)$ denotes the injection rate of shock accelerated
CRps as a function of momentum $p$ and time $t$ (see
Sect.~\ref{sec:cosmo_sim}), and $\tau_{\rm had}$ is the timescale of
hadronic losses that produce pions via CRp collisions with thermal
protons of the ICM \cite[e.g.][]{brunetti11}.
\AP{please insert formulae:}
\begin{eqnarray}
  \tau_{\rm had} = 
\end{eqnarray}

@@

We adopt a simplified isotropic MHD turbulent spectrum based on
Kraichnan's picture for the fast modes per elemental range $dk$ of the
form
\begin{equation}
  \label{eq:Wk}
  \mathcal{W}(k) =
\sqrt{2/7\,I_0\,\rho\,\langle \Vph \rangle}\,k^{-3/2},
\end{equation}
for $k_0<k<k_\rmn{cut}$. Here we adopt an injection scale of the
turbulence, $k_0= 2\upi/\lambda_0$ with $\lambda_0 =100~\mbox{kpc}$,
that is in line with previous work \citep{brunetti07,brunetti11}. Note
that this length scale defines an eddy turn-over time
$\tau_{\rmn{eddy}}\sim2\upi\lambda_0/V_0\sim1.2$~Gyr with
$V_0=500\,\rmn{km~s}^{-1}$, characteristic of a merger event.

@@

We adopt both the density \citep{1992A&A...259L..31B} and temperature
profiles \citep{2009ApJ...696.1886B,2001A&A...365L..67A} derived from
X-ray observations of the Coma cluster. They are given by:
\begin{eqnarray}
n_e &=& \frac{n_0}{\left[1+\left(R/R_{\rmn{c}}\right)^2\right]^{1.125}}\nonumber\\
k_{\rmn{B}} T &=& 8.25\,\rmn{keV} \left[1+\left(2R/R_{200}\right)^2\right]^{-0.32}\,,
\end{eqnarray}
with $n_0=3.4\times10^{-3}\,\rmn{cm}^{-3}$.  The virial and core radii
of Coma are given by $R_{200} = 2300\,\rmn{kpc}$ and $R_{\rmn{c}} =
294\,\rmn{kpc}$, respectively.

\AP{Can you please provide references for the following:} The bulk of the
CRps are injected by relatively low Mach number shocks and
parameterized by $f_\rmn{p,inj}(p) = C_\rmn{inj}\,p^{-2.5}$. The
CRps trace the thermal gas with $C_\rmn{inj} \propto
\eps_\rmn{th}^{\alpha_\rmn{CR,spat}}$, where the normalization is
fixed by assuming that the injected CR energy in the last 650~Myrs
make up 0.03\% of the thermal energy inside the virial radius, i.e.
$\int_0^{R_{200}}\eps_\rmn{p,inj} \rmn{d}
V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} =
0.0003$. The spectrum of the initial CRp distribution is determined by
the steady state between injection and cooling,
\begin{equation}
 f_\rmn{p,0} \propto \frac{\int_p^\infty f_\rmn{p,inj}(p') 
\rmn{d}p'}{\displaystyle\left|{{\rmn{d}p}\over{\rmn{d}t}}\right|_{\rm Coul}+\frac{p}{\tau_{\rm had}}}\,,
\end{equation}
where we fix the normalization by requiring
$\int_0^{R_{200}}\eps_\rmn{p,0}
\rmn{d}V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} =
0.003$. \AP{not 0.0003?} Similarly, the initial CRe distribution is
given by the steady state between cooling (Coulomb, inverse Compton,
and synchrotron) and injection of secondary CRes from $f_\rmn{p,0}$. We
also include the continuous injection of secondary CRes during
$\tau_\rmn{cl}$. The compressible turbulence responsible for
reaccelerating both the CRps and CRes is parameterized by $I_0 \propto
X_\rmn{tu} (n_{\rmn{e}} T)^{\alpha_\rmn{tu}}$. The diffusion constant
$D_{pp}$ is calculated for each radial bin using
Eqns.~\ref{eq:dpp}-\ref{eq:Gamma_e}. All parameters and assumptions
are similar to what is used for our simulated cluster.

@@

\subsection{Radio profile}
In Fig.~\ref{fig:sync_profile}, we find that all three scenarios in
which the seeds undergo Fermi-II reacceleration can reproduce the Coma
RH profile at 352~MHz. In the panel {\it Brunetti et al. (2012)} we
show that without CR streaming or a flat turbulent profile, our
simulations of reaccelerated CRs produce radio profiles that are too
steep. Indeed, even using the assumptions of previous work -- where
complete freedom in the seed population was allowed -- it is not
possible to reproduce observations in both frequencies in any
model. Note that decreasing acceleration efficiency with radius does
not change this conclusion much because of the weak radial dependence
of $D_\rmn{pp}(R)\propto
\eps_\rmn{th}(R)^{\alpha_\rmn{tu}-1}\sqrt{T(R)}$. This
signals that the problem is generic and requires either additional
modifications to the plasma physics of acceleration or a better
understanding of potential observational systematics. In addition
there are differences in the simulated density and temperature
profiles in comparison to the observed profile in Coma that impact the
CR abundance as well as cooling and reacceleration.

In principle, reacceleration via TTD leads to spectral steepening with
particle energy due to the inefficiency of the acceleration process to
counter the stronger cooling losses with increasing energy. Since
synchrotron emission peaks at frequency $\nu_\rmn{syn}\simeq 1\,
B/\umu\rmn{G} (\gamma/10^4)^2\,\rmn{GHz}$, this translates into a
spectral steepening of the radio spectrum (see
Fig.~\ref{fig:sync_spectrum}). A given radio window samples higher
energy electrons for a decreasing field strength in the cluster
outskirts. Hence, the spectral steepening with energy should translate
into a radial spectral steepening \citep{brunetti12}. However, because
of the weak dependence of the electron Lorentz factor on emission
frequency ($\gamma\propto\sqrt{\nu_\rmn{syn}}$), this effect is only
visible in our simulations for $\nu_\rmn{syn}\gtrsim5$~GHz. Most
importantly, our simulated fluid elements at a given radius sample a
broad distribution of shock history, density and temperature, which
implies very similar synchrotron brightness profiles at
$\nu_\rmn{syn}=352$~MHz and 1.4 GHz. The discrepancy of the observed
and simulated 1.4 GHz profiles could instead be due to systematic flux
calibration error in single dish observations. These could arise, for
instance, due to errors in point source subtraction. Interestingly, we
can match the 1.4 GHz data if we reduce the zero point by adding 10\%
of the central flux to every data point; this flattens the outer
profile\footnote{Lawrence Rudnick, private communication.}.
Alternatively, this may point to weaknesses in the theoretical
modeling of the particle acceleration process and may require a
stronger cutoff in the particle energy spectrum.

@@

\subsection{Radio spectrum}
\label{sect:radio_spec}
In Fig.~\ref{fig:sync_spectrum} we show that our three models that
include Fermi-II reacceleration can individually reproduce the
convexly curved total radio spectrum found in the Coma cluster. Seed
CRs in \Mstream and \Mflatturb that do not experience turbulent
reacceleration have a power-law spectrum in disagreement with
observations. In order to match both the spatial and spectral profiles
in Coma, we adopt an acceleration efficiency for the strongest shocks
in our three models \Mprimary, \Mstream, and \Mflatturb to
$\zeta_{\rmn{e}} <0.003$, $\zeta_{\rmn{p}} < 0.1$, and
$\zeta_{\rmn{p}}<0.03$, respectively. Following the Mach number
($\mathcal{M}$)-dependence of the acceleration efficiency suggested in
\cite{pinzke13}, the efficiency in weak shocks ($\mathcal{M}\sim
2.5-3.5$) that dominates the CR distribution function, has an
acceleration efficiency for protons $\zeta_{\rmn{p}}\sim0.0001-0.01$,
and for electrons $\zeta_{\rmn{e}}\sim 0.001$. Interestingly, we find
that the radio luminosity from clusters in the OFF-state (DSA only)
and ON-state (DSA and reacceleration) differ by about a factor 10 in
all our three models. However, note that for \Mprimary, the primary
CRes that generate most of the radio emission from the cluster in the
OFF-state are dominated by only a small fraction of the CRes. These
electrons are injected very recently and have not had time to cool
yet. Hence we expect there to be a large variance in the OFF-state of
different simulated clusters. As mentioned in
section~\ref{sect:param_comp}, combining radio observations with
gamma-ray limits allows us to put a lower limit to $X_\rmn{tu}$.  If
$X_\rmn{tu}$ is smaller than in our adopted models (where we assume
$X_\rmn{tu}=0.2$), then the efficiency of DSA has to be larger than
$\zeta_\rmn{p}\sim 0.1$ for the secondary CRes to reproduce the radio
observations. However, since the turbulent reacceleration acts on both
the secondary CRes and the CRps, while $\zeta_\rmn{p}$ only affects
the CRps, \Mstream and \Mflatturb would produce too much
gamma-rays. Hence we conclude that $X_\rmn{tu}\gtrsim0.2$ if all other
parameters are kept fixed. Although, we caution the reader to take
this limit too stringent because of the uncertainty in $k_0$ and
$\tau_\rmn{cl}$ that impact $X_\rmn{tu}$ for a fixed
$\tau_\rmn{D}$. This parameter space needs to be explored further in
future work in order to put more stringent limits on the level of
turbulence in clusters using radio and gamma-ray observations in
combination with turbulent reaccelerated CRs.

@@

How could we distinguish the different possibilities of a dominating
primary or secondary seed population of electrons observationally?
One possibility that is relative insensitive to adopted parameters in
our models is to use high-frequency radio observations (with e.g., the
Jansky Very Large Array) where turbulent reacceleration (which has a
high energy cutoff) is no longer efficient (see
Fig.~\ref{fig:sync_spectrum}). The negative flux bowl of the
Sunyaev-Zel'dovich effect introduces a cutoff of the RH spectrum at
frequencies above $\gtrsim 10$~GHz \citep[][ depending on cluster mass
  and redshift]{2002A&A...396L..17E,Pfrommer:2003mk}. Hence the
subdominant hadronic radio emission may only be detectable in steep
spectrum radio sources \citep{2008Natur.455..944B}, which exhibit a
cutoff at lower radio frequencies and are thought to represent dying
RHs as a result of the decaying turbulence after a
merger. Alternatively, one could attempt to reconstruct the intrinsic
high-frequency RH spectrum by filling in the missing flux due to the
Sunyaev-Zel'dovich effect by precise measurements of the Compton-$y$
parameter at microwave frequencies. Another possibility would consist
in stacking the radio data of radio-quiet clusters that due not
exhibit RH emission \citep{2011ApJ...740L..28B}. This may reveal the
glow of radio emission due to steady state secondary
population. Emission from faint secondary electrons should still be
visible, whereas due to the much more intermittent nature of DSA
injection, primary CRe will instead show a sharp cutoff due to
cooling, and will not be visible at high energies (see
Fig.~\ref{fig:sync_spectrum}). We will pursue further implications and
distinguishing characteristics of these competing models in future
work.

>>>>

Given a seed population of CRs, we adopt essentially the same set of
plasma physics assumptions as the reacceleration model for RHs
\citep{brunetti07,brunetti11}. We solve the isotropic, gyro-phase
averaged Fokker-Planck equation (via a Crank-Nicholson scheme) for the
time evolution of the CRe distribution in the Lagrangian frame
\citep{brunetti07,brunetti11}:
\begin{eqnarray}
{{d f_{\rmn{e}}(p,t)}\over{d t}} &\!=&
\frac{\partial}{\partial p}
\left\{
f_{\rmn{e}}(p,t)\left[
\left|\frac{dp}{dt}\right|_{\rm Coul} 
+ \frac{p}{3}\left(\bnabla\bcdot \bvel\right)
+ \left|\frac{dp}{dt}\right|_{\rm rad}\right.\right.
\nonumber\\
&-& \left.\left.{1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right) 
\right]\right\} - \left(\bnabla\bcdot \bvel\right) f_{\rmn{e}}(p,t)
\nonumber\\
&+& {{\partial^2 }\over{\partial p^2}}
\left[
D_{pp} f_{\rmn{e}}(p,t) \right]+ Q_{\rmn{e}}\left[p,t;f_{\rmn{p}}(p,t)\right]   \, .
\label{elettroni}
\end{eqnarray}
Here $f_{\rmn{e}}$ is the one-dimensional distribution in position $x$
(suppressed for clarity), momentum $p$ and time $t$ (which is
normalized such that the number density is given by
$n_{\rmn{e}}(t)=\int d p f_{\rmn{e}}(p,t)$), $d/dt=\partial/\partial
t+\bvel\bcdot\bnabla$ is the Lagrangian derivative, $\bvel$ is the gas
velocity, $|dp/dt|$ represents radiative
\citep[rad,][]{1979rpa..book.....R} and Coulomb
\citep[Coul,][]{1972Phy....60..145G} losses, \AP{please insert
  formulae: -- done}
\begin{eqnarray}
   \left|\frac{dp}{dt}\right|_{\rm Coul} &=& \frac{3\,\sigma_\rmn{T}\,n_e\,c}{2\, \beta^2}
  \left[\ln\left(\frac{m_e c^2 \beta \sqrt{\gamma-1}}{\hbar\,\omega_\rmn{plasma}}\right)\right.\nonumber \\
    &-&\ln(2)\left(\frac{\beta^2}{2}+\frac{1}{\gamma}\right)+\frac{1}{2}+
    \left.\left(\frac{\gamma-1}{4\gamma}\right)^2\right]\,, \\
  \rmn{where} &\,& \beta = p/\sqrt{1+p^2}\,,\qquad \gamma=\sqrt{1+p^2}\,, \quad\rmn{and}\nonumber \\
  \left|\frac{dp}{dt}\right|_{\rm rad~} &=& \frac{4}{3}\frac{\sigma_\rmn{T}}{m_ec}\,
  \frac{p^2}{\beta}\,\left[1+\left(\frac{B}{B_\rmn{CMB}}\right)^2\right]\,.
\end{eqnarray}
Here $\omega_\rmn{plasma} = \sqrt{4\pi e^2 n_e / m_e}$ is the plasma
frequency, $n_e$ is the number density of free electrons, and
$\sigma_\rmn{T}= 8\pi e^4/3(m_e c^2)^2$ is the Thomson cross
section. The {\it rms} magnetic field strength is denoted by $B$ and
the equivalent field strength of the cosmic-microwave background is
given by $B_\rmn{CMB} = 3.24 (1 + z)^2\mu\rmn{G}$, where $z$ denotes
the redshift. In the peripheral cluster regions, where $B <<
B_\rmn{CMB}$, the CRes loose virtually all their energy by means of
inverse Compton emission. $D_{pp}$ is the momentum space diffusion
coefficient (see Sect.~\ref{sec:reacc}), and $Q_{\rmn{e}}$ denotes the
injection rate of primary and secondary electrons in the ICM (see
Sect.~\ref{sec:cosmo_sim}). The first term containing the expression
$\bnabla\bcdot \bvel$ represents Fermi-I acceleration and the second
term of this form describes adiabatic gains and losses.

@@

The time evolution of the spectral energy distribution of CRps,
$f_{\rmn{p}}$, is similarly given by:
\begin{eqnarray}
\lefteqn{
  {{d f_{\rmn{p}}(p,t)}\over{d t}} =
  {{\partial }\over{\partial p}}
  \left\{
  f_{\rmn{p}}(p,t)\left[ \left|{{dp}\over{dt}}\right|_{\rm Coul}
    + \frac{p}{3}\bnabla\bcdot \left(\bvel+\bvel_{\rmn{st}}\right)\right.\right.}
\nonumber\\
&&-\left.\left. {1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right)
\right]\right\} - f_{\rmn{p}}(p,t) \bnabla\bcdot \left(\bvel+\bvel_{\rmn{st}}\right) 
- \bvel_{\rmn{st}}\bcdot\bnabla f_{\rmn{p}}(p,t)
\nonumber\\
&&+\,\,\, {{\partial^2 }\over{\partial p^2}}
\left[ D_{pp} f_{\rmn{p}}(p,t) \right] - {{f_{\rmn{p}}(p,t)}\over{\tau_{\rm had}(p)}}
+ Q_{\rmn{p}}(p,t)\, ,
\label{eq:FP_p}
\end{eqnarray}
where $\bvel_{\rmn{st}}=-\varv_{\rmn{A}}\bnabla f_{\rmn{p}}/|\bnabla
f_{\rmn{p}}|$ is the streaming velocity in the isotropic transport
approximation, $\varv_{\rmn{A}}$ is the Alfv\'en speed,
and $Q_{\rmn{p}}(p,t)$ denotes the injection rate of shock accelerated
CRps as a function of momentum $p$ and time $t$ (see
Sect.~\ref{sec:cosmo_sim}). The timescale of
hadronic losses that produce pions via CRp collisions with thermal
protons of the ICM is given by 
\AP{please insert formulae: -- done}
\begin{eqnarray}
  \tau_{\rm had} = \frac{1}{c\,n_\rmn{th}\,\sigma^{+/-,0}(p)}\,
\end{eqnarray}
where we use the cross-section, $\sigma^{+/-,0}(p)$, given by the
fitting formula in \citep{1986ApJ...307...47D}.

@@

We adopt a simplified isotropic MHD turbulent spectrum based on
Kraichnan's picture for the fast modes per elemental range $dk$ of the
form
\begin{equation}
  \label{eq:Wk}
  \mathcal{W}(k) =
\sqrt{2/7\,I_0\,\rho\,\langle \Vph \rangle}\,k^{-3/2},
\end{equation}
for $k_0<k<k_\rmn{cut}$. Here we adopt an injection scale of the
turbulence, $k_0= 2\upi/\lambda_0$ with $\lambda_0 =100~\mbox{kpc}$,
that is in line with previous work
\citep{2006MNRAS.366.1437S,brunetti07,brunetti11}. Note that this
length scale defines an eddy turn-over time
$\tau_{\rmn{eddy}}\sim2\upi\lambda_0/V_0\sim1.2$~Gyr with
$V_0=500\,\rmn{km~s}^{-1}$, characteristic of a merger event.

@@

We adopt both the density \citep{1992A&A...259L..31B} and temperature
profiles \citep{2009ApJ...696.1886B,2001A&A...365L..67A} derived from
X-ray observations of the Coma cluster. They are given by:
\begin{eqnarray}
n_e &=& \frac{n_0}{\left[1+\left(R/R_{\rmn{c}}\right)^2\right]^{1.125}}\nonumber\\
k_{\rmn{B}} T &=& 8.25\,\rmn{keV} \left[1+\left(2R/R_{200}\right)^2\right]^{-0.32}\,,
\end{eqnarray}
with $n_0=3.4\times10^{-3}\,\rmn{cm}^{-3}$.  The virial and core radii
of Coma are given by $R_{200} = 2300\,\rmn{kpc}$
\citep{2002ApJ...567..716R} and $R_{\rmn{c}} = 294\,\rmn{kpc}$,
respectively.

\AP{Can you please provide references for the following: -- check if
  ok, the numbers are taken from our simulated g72a cluster. It should
  be more clear now...} The bulk of the CRps are injected by
relatively low Mach number shocks and parameterized by
$f_\rmn{p,inj}(p) = C_\rmn{inj}\,p^{-\alpha_\rmn{inj}}$, where
$\alpha_\rmn{inj}\approx 2.5$ in our simulations. The CRps
approximately trace the thermal gas with $C_\rmn{inj} \propto
\eps_\rmn{th}^{\alpha_\rmn{CR,spat}}$
\citep{pinzke10,2016MNRAS.459...70V}, where the normalization is fixed
by the injected CR energy in the last 650~Myrs. Our simulations show
that it roughly make up 0.03\% of the thermal energy inside the virial
radius, i.e.  $\int_0^{R_{200}}\eps_\rmn{p,inj} \rmn{d}
V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} =
0.0003$. The spectrum of the initial CRp distribution is determined by
the steady state between injection and cooling,
\begin{equation}
 f_\rmn{p,0} \propto \frac{\int_p^\infty f_\rmn{p,inj}(p') 
\rmn{d}p'}{\displaystyle\left|{{\rmn{d}p}\over{\rmn{d}t}}\right|_{\rm Coul}+\frac{p}{\tau_{\rm had}}}\,,
\end{equation}
where we fix the normalization by requiring
$\int_0^{R_{200}}\eps_\rmn{p,0}
\rmn{d}V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} =
0.003$. \AP{not 0.0003? -- No, the injected energy in the last 650 Mys
  is smaller then the energy density of the CRs injected during the
  formation of the cluster. I estimated the difference to be about a
  factor 10.} Similarly, the initial CRe distribution is given by the
steady state between cooling (Coulomb, inverse Compton, and
synchrotron) and injection of secondary CRes from $f_\rmn{p,0}$. We
also include the continuous injection of secondary CRes during
$\tau_\rmn{cl}$. The compressible turbulence responsible for
reaccelerating both the CRps and CRes is parameterized by $I_0 \propto
X_\rmn{tu} (n_{\rmn{e}} T)^{\alpha_\rmn{tu}}$. The diffusion constant
$D_{pp}$ is calculated for each radial bin using
Eqns.~\ref{eq:dpp}-\ref{eq:Gamma_e}. All parameters and assumptions
are similar to what is used for our simulated cluster.

@@

\subsection{Radio profile}
In Fig.~\ref{fig:sync_profile}, we find that all three scenarios in
which the seeds undergo Fermi-II reacceleration can reproduce the Coma
RH profile at 352~MHz. \AP{It is also clear that without turbulent
  reacceleration, the simulated radio profiles are too steep.} In the
panel {\it Brunetti et al. (2012)} we show that without CR streaming
or a flat turbulent profile, our simulations of reaccelerated CRs
produce radio profiles that are too steep. Indeed, even using the
assumptions of previous work -- where complete freedom in the seed
population was allowed -- it is not possible to reproduce observations
in both frequencies in any model. Note that decreasing acceleration
efficiency with radius does not change this conclusion much because of
the weak radial dependence of $D_\rmn{pp}(R)\propto
\eps_\rmn{th}(R)^{\alpha_\rmn{tu}-1}\sqrt{T(R)}$. This signals that
the problem is generic and requires either additional modifications to
the plasma physics of acceleration or a better understanding of
potential observational systematics. In addition there are differences
in the simulated density and temperature profiles in comparison to the
observed profile in Coma that impact the CR abundance as well as
cooling and reacceleration.

In principle, reacceleration via TTD leads to spectral steepening with
particle energy due to the inefficiency of the acceleration process to
counter the stronger cooling losses with increasing energy. Since
synchrotron emission peaks at frequency $\nu_\rmn{syn}\simeq 1\,
B/\umu\rmn{G} (\gamma/10^4)^2\,\rmn{GHz}$, this translates into a
spectral steepening of the radio spectrum (see \AP{the left panel of
  Fig.~\ref{fig:sync_spectrum}} where the continuous injection of
secondary CRes is absent). A given radio window samples higher energy
electrons for a decreasing field strength in the cluster
outskirts. Hence, the spectral steepening with energy should translate
into a radial spectral steepening \citep{brunetti12}. However, because
of the weak dependence of the electron Lorentz factor on emission
frequency ($\gamma\propto\sqrt{\nu_\rmn{syn}}$), this effect is only
visible in our simulations for $\nu_\rmn{syn}\gtrsim5$~GHz. Most
importantly, our simulated fluid elements at a given radius sample a
broad distribution of shock history, density and temperature, which
implies very similar synchrotron brightness profiles at
$\nu_\rmn{syn}=352$~MHz and 1.4 GHz. The discrepancy of the observed
and simulated 1.4 GHz profiles could instead be due to systematic flux
calibration error in single dish observations. These could arise, for
instance, due to errors in point source subtraction. Interestingly, we
can match the 1.4 GHz data if we reduce the zero point by adding 10\%
of the central flux to every data point; this flattens the outer
profile\footnote{Lawrence Rudnick, private communication.}.
Alternatively, this may point to weaknesses in the theoretical
modeling of the particle acceleration process and may require a
stronger cutoff in the particle energy spectrum.

@@

\subsection{Radio spectrum}
\label{sect:radio_spec}
In Fig.~\ref{fig:sync_spectrum} we show that our three models that
include Fermi-II reacceleration can individually reproduce the
convexly curved total radio spectrum found in the Coma cluster. Seed
CRs in \Mstream and \Mflatturb that do not experience turbulent
reacceleration have a power-law spectrum in disagreement with
observations. In order to match both the spatial and spectral profiles
in Coma, we adopt an acceleration efficiency for the strongest shocks
in our three models \Mprimary, \Mstream, and \Mflatturb to
$\zeta_{\rmn{e}} <0.003$, $\zeta_{\rmn{p}} < 0.1$, and
$\zeta_{\rmn{p}}<0.03$, respectively. Following the Mach number
($\mathcal{M}$)-dependence of the acceleration efficiency suggested in
\cite{pinzke13}, the efficiency in weak shocks ($\mathcal{M}\sim
2.5-3.5$) that dominates the CR distribution function, has an
acceleration efficiency for protons $\zeta_{\rmn{p}}\sim0.0001-0.01$,
and for electrons $\zeta_{\rmn{e}}\sim 0.001$. Interestingly, we find
that the radio luminosity from clusters in the OFF-state (DSA only)
and ON-state (DSA and reacceleration) differ by about a factor 10-20
in all our three models. \AP{This means that the secondary CRes are
  dominated by the reaccelerated fossil CRes and not from the CRes
  produced by reaccelerated CRps. However, for high frequencies
  ($\nu_\rmn{syn}\gtrsim$ GHz) where synchrotron cooling is more
  efficient than reacceleration, the emission is dominated by the CRes
  produced in the continuous injection of electrons from reaccelerated
  CRps. It is also worth mentioning that the radio emission from
  secondary CRes are smoothly distributed around the cluster because
  of the continuous injection, hence the it is not dominated by
  outliers.} However, \sout{note that} for \Mprimary, the primary CRes
that generate most of the radio emission from the cluster in the
OFF-state are dominated by only a small fraction of the CRes. These
electrons are injected very recently and have not had time to cool
yet. Hence we expect there to be a large variance in the OFF-state of
different simulated clusters. As mentioned in
section~\ref{sect:param_comp}, combining radio observations with
gamma-ray limits allows us to put a lower limit to $X_\rmn{tu}$.  If
$X_\rmn{tu}$ is smaller than in our adopted models (where we assume
$X_\rmn{tu}=0.2$), then the efficiency of DSA has to be larger than
$\zeta_\rmn{p}\sim 0.1$ for the secondary CRes to reproduce the radio
observations. However, since the turbulent reacceleration acts on both
the secondary CRes and the CRps, while $\zeta_\rmn{p}$ only affects
the CRps, \Mstream and \Mflatturb would produce too much
gamma-rays. Hence we conclude that $X_\rmn{tu}\gtrsim0.2$ if all other
parameters are kept fixed. Although, we caution the reader to take
this limit too stringent because of the uncertainty in $k_0$ and
$\tau_\rmn{cl}$ that impact $X_\rmn{tu}$ for a fixed
$\tau_\rmn{D}$. This parameter space needs to be explored further in
future work in order to put more stringent limits on the level of
turbulence in clusters using radio and gamma-ray observations in
combination with turbulent reaccelerated CRs.

@@

How could we distinguish the different possibilities of a dominating
primary or secondary seed population of electrons observationally?
\AP{I do not understand the next scentence, could you clarify?} One
possibility that is relative insensitive to adopted parameters in our
models is to use high-frequency radio observations (with e.g., the
Jansky Very Large Array) where turbulent reacceleration (which has a
high energy cutoff) is no longer efficient (see
Fig.~\ref{fig:sync_spectrum}). The negative flux bowl of the
Sunyaev-Zel'dovich effect introduces a cutoff of the RH spectrum at
frequencies above $\gtrsim 10$~GHz \citep[][ depending on cluster mass
  and redshift]{2002A&A...396L..17E,Pfrommer:2003mk}. Hence the
subdominant \sout{hadronic} radio emission \AP{from freshly injected
  secondary CRes} may only be detectable in steep spectrum radio
sources \citep{2008Natur.455..944B}, which exhibit a cutoff at lower
radio frequencies and are thought to represent dying RHs as a result
of the decaying turbulence after a merger. Alternatively, one could
attempt to reconstruct the intrinsic high-frequency RH spectrum by
filling in the missing flux due to the Sunyaev-Zel'dovich effect by
precise measurements of the Compton-$y$ parameter at microwave
frequencies. Another possibility would consist in stacking the radio
data of radio-quiet clusters that do not exhibit RH emission
\AP{individually} \citep{2011ApJ...740L..28B}. This may reveal the
glow of radio emission due to steady state secondary
population. Emission from faint secondary electrons should still be
visible, whereas due to the much more intermittent nature of DSA
injection, primary CRe will instead show a sharp cutoff due to
cooling, and will not be visible at high energies (see
Fig.~\ref{fig:sync_spectrum}). \AP{Finally we want to mention that in
  the near future we hope to gain valuable information about the
  turbulent profile in galaxy clusters from the recently launched
  X-ray satellite ASTRO-H. Alternatively, as magnetohydrodynamic
  simulations improve, these can provide valuable insight about the
  profile and the total energy of turbulence in clusters. This will
  further help us to distinguish the three different models from each
  other.} We will pursue further implications and distinguishing
characteristics of these competing models in future work.
